GeckoGraph: A Visual Language for Polymorphic Types

### 2025-04-09 main.tex
Updates from Overleaf
typo

We illustrate the task of the user study using levels 2 and 3of the game. At level 2 (Fig. \ref{fig:level-example}), the players need to implement the function \texttt{ zeroToHero :: Zero a -> Hero b}. The available functions are \texttt{runZero::Zero a -> a}, \texttt{makeHero:: a -> Hero a}. A generic function \texttt{(\$)} is provided to improve the ergonomics of composing functions, but all tasks can be completed without the use of generic functions. The possible solution and other details of the level can be found in the appendix (Appendix \ref{levels}). To complete this level, players only need to use each of the provided function once. The implementation {\tt zeroToHero z = makeHero (runZero z)} is one possible solution.

@@

\appendix
\section{Game levels} \label{levels}
We provide all the level settings we used in our user study. The online game is still open source and available for evaluation \cite{Anonymous_undated-ne}. However, this can be attempted locally with a Haskell interpreter or even with a pen and paper. The target type is the desired type signature for the function \texttt{zeroToHero}. The available functions show a list of functions that are allowed to be used in the implementation. It is not required to use all the available functions, and it is not forbidden to use any other functions or variables outside the provided functions; even the Haskell prelude is not available.

>>>>

We illustrate the task of the user study using levels 2 and 3 of the game. At level 2 (Fig. \ref{fig:level-example}), the players need to implement the function \texttt{ zeroToHero :: Zero a -> Hero b}. The available functions are \texttt{runZero::Zero a -> a}, \texttt{makeHero:: a -> Hero a}. A generic function \texttt{(\$)} is provided to improve the ergonomics of composing functions, but all tasks can be completed without the use of generic functions. The possible solution and other details of the level can be found in the appendix (Appendix \ref{levels}). To complete this level, players only need to use each of the provided function once. The implementation {\tt zeroToHero z = makeHero (runZero z)} is one possible solution.

@@

\appendix
\section{Game levels} \label{levels}
We provide all the level settings we used in our user study. The online game is open source and available for evaluation \cite{Anonymous_undated-ne}. However, this can be attempted locally with a Haskell interpreter or even with a pen and paper. The target type is the desired type signature for the function \texttt{zeroToHero}. The available functions show a list of functions that are allowed to be used in the implementation. It is not required to use all the available functions, and it is not forbidden to use any other functions or variables outside the provided functions; even the Haskell prelude is not available.
